\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/experiments.tex
Pivot perf_summary table

\begin{table}
\todo{Consider switching to graph, or changing table layout..not very intuitive right now.}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations relative to results when imputing on base table. Values of $0.0$,
    $100.0$, or $NaN$ indicate uninformative values\todo{use one flag value (-) or explain why value is uninformative}.} %TODO MJS
\label{table:smape}
\end{table}

>>>>

\begin{table}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations relative to results when imputing on base table. Queries optimized for quality ($\alpha=0$) generally achieve lower error than queries optimized for efficiency ($\alpha=1$).}
\label{table:smape}
\end{table}
